Visualizing Physical Query Execution in a Relational Big Data Management System

### 2014-02-27 progress-report/abstract.tex
move footnote

In particular, our visualization system is built to inspect query execution in Myria, a distributed big data management system currently being developed in the UW CSE database group. Myria aims towards building a distributed database platform to provide \emph{big data management and analytics as a service} primarily for scientific applications.

>>>>

In particular, our visualization system is built to inspect query execution in Myria\footnote{\url{http://myria.cs.washington.edu/}}, a distributed big data management system currently being developed in the UW CSE database group. Myria aims towards building a distributed database platform to provide \emph{big data management and analytics as a service} primarily for scientific applications.

### 2014-02-27 progress-report/project_plan.tex
move footnote

Dominik built a prototype last quarter for the \emph{Distributed Systems} class. The goal of this project was to build a system to collect and analyze logs in the Myria \footnote{\url{http://myria.cs.washington.edu/}} system. The prototype allows a user to switch between three levels of query execution visualization to identify the problem at the granularity that best reveals the information they need. The goal for this project is to improve the visualization part of the previous prototype and build a more consistent exploration tool. Furthermore, the back end has to be rewritten to support visualization of long running queries in the Myria system but are not supported in the current prototype.

@@

\begin{enumerate}
    \item Project Planning (completed Feb 23rd)
    \begin{enumerate}
        \item Brainstorming and goals
        \item List questions we'd like to answer
        \item Develop a consistent story-board
        \item Assign responsibilities
    \end{enumerate}
    \item Initial System Setup \& Specifications (completed Feb 23rd)
    \begin{enumerate}
        \item Set up cluster \& web front-end
        \item Data collection from query-runs
        \item Formalize interfaces and data formats
    \end{enumerate}

\end{enumerate}

>>>>

Dominik built a prototype last quarter for the \emph{Distributed Systems} class. The goal of this project was to build a system to collect and analyze logs in the Myria system. The prototype allows a user to switch between three levels of query execution visualization to identify the problem at the granularity that best reveals the information they need. The goal for this project is to improve the visualization part of the previous prototype and build a more consistent exploration tool. Furthermore, the back end has to be rewritten to support visualization of long running queries in the Myria system but are not supported in the current prototype.

@@

\begin{enumerate}
    \item Project Planning (completed Feb 23rd)
    \begin{enumerate}
        \item Brainstorming and goals
        \item List questions we'd like to answer
        \item Develop a consistent story-board
        \item Assign responsibilities
    \end{enumerate}
    \item Initial System Setup \& Specifications (completed Feb 23rd)
    \begin{enumerate}
        \item Set up cluster \& web front-end
        \item Data collection from query-runs
        \item Formalize interfaces and data formats
    \end{enumerate}
    \item Initial Prototype (complete by March 5th)
    \begin{enumerate}
        \item Produce initial visualizations
        \item Add a basic interaction between views
    \end{enumerate}
    \item Working Prototype (complete by March 13th)
    \begin{enumerate}
        \item Improve visualizations and interaction
    \end{enumerate}
    \item Project Deliverables 
    \begin{enumerate}
        \item Produce poster (complete by March 13th)
        \item Complete demo (complete by March 13th)
        \item Write the project report (complete by March 20th)
    \end{enumerate}
\end{enumerate}
